Introduction to Task Views for Private Use
========================================================

CRAN Task Views let you handle CRAN packages into a unit of task view. A task view has one or more packages. `ctv` package enables you to install or update packages listed in the view.

```{r}
library(ctv)
```

Functions in `ctv` are similar to the functions for packages.

Action | Packages | Views
------ | -------- | -----
Search | `available.packages` | `available.views` 
Installation | `install.packages` | `install.views`
Removal | `remove.packages` | *NA*
Update | `update.packages` | `update.views`
Download | `download.packages` | `download.views`
Listing installed | `installed.packages` | *NA*

```{r}
available.views()
```

**Notice**: Each official view contains so many packages. Do not try to install or download view unless you really want to install it.

Creating Your View
--------------------------------------------------

You can define your favorite packages into a view in an XML format. Here's an example.

```
<?xml version="1.0" encoding="UTF-8"?>
<CRANTaskView>
  <name>MyView</name>
  <topic>My Favorite Packages.</topic>
  <maintainer email="mail@example.com">kos59125</maintainer>
  <version>2012-06-15</version>
  <info>Just listed a couple of random pakcages.</info>
  <packagelist>
    <pkg priority="core">rbenchmark</pkg>
    <pkg>RUnit</pkg>
  </packagelist>
  <links>
    <a href="http://cran.r-project.org/web/packages/ctv/vignettes/ctv-howto.pdf">Writing CRAN Task Views</a>
    <a href="http://cran.r-project.org/web/views/">CRAN Task Views</a>
  </links>
</CRANTaskView>
```

See vignettes of `ctv` package to get details.

The file is able to be read using `read.ctv` function.

```{r}
myview <- read.ctv("myview.ctv")
myview
```

Use Your View
--------------------------------------------------

You cannot describe your favorite CRAN server in ctv files. Because `repos` argument in `install.views` function, unfortunately, does not work fine, you'll get an error.

```{r}
install.views(myview, repos="http://cran.r-project.org/")
```

To solve the problem, you can enforce the view object to have `repository` attribute.

```{r}
myview$repository <- "http://cran.r-project.org"
print(myview)
```

OK, the repository is surely set in the view. Try to install again.

```{r message=FALSE}
install.views(myview)
```

Congraturations! You no longer get annoyed with troublesome setup of packages.
